Generate data for NOBA cod ensemble modeling

### 2020-06-01 NOBAcod.Rmd
add figs for annage from wrappers

#add this to om_indices function so that this has years when read in
fish_age_comp$time <- as.integer(floor(fish_age_comp$time/fstepperyr))

@@

#add this to om_indices function so that this has years when read in
fish_age_comp$time <- as.integer(floor(fish_age_comp$time/fstepperyr))

Natage <- filter(fish_age_comp, time %in% c(55:175))

@@

@@

#### Survey age composition (annual ages)
```{r plot-annagecomp}

@@

@@

>>>>

Natage <- filter(age_comp_data, time %in% c(150:270))

@@

#read in comp data
fish_age_comp <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsAgeComp.rds")))
fish_age_comp <- fish_age_comp[[1]]

Natage <- filter(fish_age_comp, time %in% c(30:53))

@@

  Natageplot + facet_wrap(~time, ncol=6, scales="free_y")
```

@@

#### Survey age composition (annual ages)
```{r plot-annagecomp}
#read in comp data
annage_comp_data <- readRDS(file.path(d.name, paste0(scenario.name, "survObsFullAgeComp.rds")))
annage_comp_data <- annage_comp_data[[1]]

Natage <- filter(annage_comp_data, time %in% c(150:270))

@@

fish_annage_comp <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsFullAgeComp.rds")))
fish_annage_comp <- fish_annage_comp[[1]]

#add this to om_indices function so that this has years when read in
fish_annage_comp$time <- fish_annage_comp$time/fstepperyr

Catage <- filter(fish_annage_comp, time %in% c(30:53))

  Catageplot + facet_wrap(~time, ncol=6, scales="free_y")
```

@@

Note: NOBA doesn't seem to have a selective fishery for cod. Lots of age 1 in the catch!
